Light versus dark in strong-lens galaxies: Dark matter haloes that are rounder than their stars

### 2015-09-29 shapes/paper.tex
small edits

The non-parametric mass models themselves are constructed using the \Glass\ framework for modelling multiple-image lenses \citep{2014MNRAS.445.2181C}. \Glass\ produces ensembles of mass maps, each of which reproduces exactly the observed image positions, image parities and time delays (if measured). The lensing data must be in the form of point images, which could be quasars or simply point-like features in otherwise extended images, but this was not a problem for the lenses studied in this work. The estimated stellar mass (explained below in Section~\ref{sec:data}) is taken as a lower limit on the total mass. The additional mass that needs to be put on top, in order to reproduce the lensing observables, is interpreted as dark matter. The lensing observables and assumed non-negative dark matter by themselves leave the mass distribution under-determined. Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the same shape). The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C} \citep[alternatively, for a more intuitive account of \Glass\ see Section~3.2 of][]{2015MNRAS.447.2170K}. Tests of how well the shape can be recovered from lensing data are given in Section~5.2 and Figure~8 of \citet{2014MNRAS.445.2181C}.

@@

@@

Figure~\ref{fig:wedgesradii} is similar to Figure~\ref{fig:wedgesall} with the difference that shapes are now averaged within different multiples of $R_e$. As the inertia tensor defined in Eq.~\ref{eq:inertiatensor} scales depends on the square of the radius, averaging up to different limiting radii could potentially yield different results. We observe that the shape estimator is robust to these changes. However, we note that there appears to be a slight trend that the ellipticity of the stellar distribution increases with increasing radius of enclosure. Whether this trend persists with data of a higher quality remains to be seen. There is potentially a similar trend for the dark matter distribution, although the samples are consistent with a constant ellipticity as well. {\it0957}, and to some degree {\it1422}, display, however, some signs of isophotal twist complicating the interpretation (see Appendix).

@@

Figure~\ref{fig:thetascatter} shows the degeneracy between the position angles of the dark matter halo $\theta_{dm}$ and the external shear $\theta_{g}$ for each strong lens galaxy. We note that the constraints on the direction of the external shear are stronger than on the dark matter distribution. There is a slight degeneracy between the two quantities, it can however for most lenses be largely broken. \textbf{CB: Do we need more here, i.e. on why this degeneracy can be broken?}

>>>>

The non-parametric mass models themselves are constructed using the \Glass\ framework for modelling multiple-image lenses \citep{2014MNRAS.445.2181C}. \Glass\ produces ensembles of mass maps, each of which reproduces exactly the observed image positions, image parities and time delays (if measured). The lensing data must be in the form of point images, which could be quasars or simply point-like features in otherwise extended images, but this was not a problem for the lenses studied in this work. The estimated stellar mass (explained below in Section~\ref{sec:data}) is taken as a lower limit on the total mass. The additional mass that needs to be put on top, in order to reproduce the lensing observables, is interpreted as dark matter. The lensing observables and assumed non-negative dark matter by themselves leave the mass distribution under-determined. Hence, an additional prior is used, requiring the mass distribution to be centrally concentrated, with the same centre as the galaxy light (but not necessarily the same shape). The precise formulation of the prior is given in Section~3 of \citet{2014MNRAS.445.2181C} \citep[alternatively, for a more intuitive account of \Glass\ see Section~3.2 of][]{2015MNRAS.447.2170K}.

@@

Most relevant to the present work are Section~5.2 and Figure~8 of
\citet{2014MNRAS.445.2181C}, showing the recovery of
$\lambda_2/\lambda_1$.  The typical errors in this quantity are
10--20\%.

@@

Figure~\ref{fig:wedgesradii} is similar to Figure~\ref{fig:wedgesall} with the difference that shapes are now averaged within different multiples of $R_e$. As the inertia tensor defined in Eq.~\ref{eq:inertiatensor} scales depends on the square of the radius, averaging up to different limiting radii could potentially yield different results. We observe that the shape estimator is robust to these changes. However, we note that there appears to be a slight trend that the ellipticity of the stellar distribution increases with increasing radius of enclosure. Whether this trend persists with data of a higher quality remains to be seen. There is potentially a similar trend for the dark matter distribution, although the samples are consistent with a constant ellipticity as well. {\it0957}, and to some degree {\it1422}, display, however, some signs of isophotal twist complicating the interpretation (see Appendix \ref{sec:shearshapedeg}).

@@

Figure~\ref{fig:thetascatter} shows the degeneracy between the position angles of the dark matter halo $\theta_{dm}$ and the external shear $\theta_{g}$ for each strong lens galaxy. We note that the constraints on the direction of the external shear are stronger than on the dark matter distribution. There is a weak degeneracy between the two quantities, it can however for most lenses be largely broken.  This is expected, since internal ellipticity and external shear tend to have similar effects, but are not an exact degeneracy \cite[cf.][]{1999A&A...349..108D}.
